---
title: "Sightseeing in Berlin"
author: "Kristóf Sz."
date: '2021 03 05 '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Berlin

I was in Berlin first in 2016 and this city of Europe, which is the capital of Germany, is so beautiful, that I would like to give you some tipps. The list of sightseeings you must see:

- Brandenburger Tor
- Bebel PLatz
- Pergamonmuseum
- Reichstag
- Berliner Dom
- Checkpoint Charlie
- Siegessäule
- Alexanderplatz
- Zoologischer Garten Berlin
- Kaiser Wilhelm-Gedächtnis-Kirche
- Gedenkstätte Berliner Mauer (Bernauer Straße)
- Unter den Linden

```{r, echo=FALSE}
library(knitr)
library(leaflet)

plots<-list.files('.', pattern="*.jpg",
                  full.names = TRUE)

include_graphics(plots[1:4])
include_graphics(plots[5:8])
include_graphics(plots[9:12])
```


And where can be found these places?

```{r, echo=FALSE, comment=""}
df<-data.frame(name=c("Brandenburger Tor","Bebel Platz",
                       "Pergamonmuseum","Reichstag",
                       "Berliner Dom","Checkpoint Charlie",
                       "Siegessäule","Alexanderplatz",
                       "Zoologischer Garten Berlin",
                       "Kaiser Wilhelm-Gedächtnis-Kirche",
                       "Gedenkstätte Berliner Mauer (Bernauer Straße)",
                       "Unter den Linden"),
                lat=c(52.516470214977964,
                      52.516848208354396,
                      52.52133796257648,
                      52.51909935186394,
                      52.51953616289787,
                      52.50788023094092,
                      52.5149479910393,
                      52.52273564746541,
                      52.50857173302999,
                      52.5052271286444,
                      52.53585514586697,
                      52.51702409964071),
                lng=c(13.378033935341255,
                      13.394927707130133,
                      13.398073770840258,
                      13.377345676236637,
                      13.401902336703582,
                      13.391531593945635,
                      13.351529856914164,
                      13.416349312475248,
                      13.339935682917975,
                      13.3365904287116,
                      13.39096850258321,
                      13.390017891182145),
                type=c("building","building",
                       "museum","building",
                       "church","history",
                       "history","building"
                       ,"zoo","church",
                       "history","street"))

df$type<-as.factor(df$type)

factpal <- colorFactor(topo.colors(5), df$type)



df %>% leaflet() %>% addTiles() %>% 
        addCircleMarkers(lat = ~lat, lng = ~lng,
                         color = ~factpal(type),
                         label = ~name,
                         clusterOptions = markerClusterOptions()) %>%
        addLegend(pal = factpal, value=~type)

```

The code for the previous map:

```{r, echo=TRUE, eval=FALSE, comment=""}
df<-data.frame(name=c("Brandenburger Tor","Bebel Platz",
                       "Pergamonmuseum","Reichstag",
                       "Berliner Dom","Checkpoint Charlie",
                       "Siegessäule","Alexanderplatz",
                       "Zoologischer Garten Berlin",
                       "Kaiser Wilhelm-Gedächtnis-Kirche",
                       "Gedenkstätte Berliner Mauer (Bernauer Straße)",
                       "Unter den Linden"),
                lat=c(52.516470214977964,
                      52.516848208354396,
                      52.52133796257648,
                      52.51909935186394,
                      52.51953616289787,
                      52.50788023094092,
                      52.5149479910393,
                      52.52273564746541,
                      52.50857173302999,
                      52.5052271286444,
                      52.53585514586697,
                      52.51702409964071),
                lng=c(13.378033935341255,
                      13.394927707130133,
                      13.398073770840258,
                      13.377345676236637,
                      13.401902336703582,
                      13.391531593945635,
                      13.351529856914164,
                      13.416349312475248,
                      13.339935682917975,
                      13.3365904287116,
                      13.39096850258321,
                      13.390017891182145),
                type=c("building","building",
                       "museum","building",
                       "church","history",
                       "history","building"
                       ,"zoo","church",
                       "history","street"))

df$type<-as.factor(df$type)

factpal <- colorFactor(topo.colors(5), df$type)



df %>% leaflet() %>% addTiles() %>% 
        addCircleMarkers(lat = ~lat, lng = ~lng,
                         color = ~factpal(type),
                         label = ~name,
                         clusterOptions = markerClusterOptions()) %>%
        addLegend(pal = factpal, value=~type)

```

I hope that this little tour has picqued you interest and made you feel to visit Berlin.
